--- 
title: "The Community Manager’s Survival Guide"
author: "The AAAS Community Engagment Fellows and Staff"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "A collection of stories about career paths and checklist for day-to-day activities to help you survive and thrive as a scientific community manager."
---

# Introduction

The [AAAS Community Engagement Fellows Program (CEFP)](https://www.aaas.org/programs/community-engagement-fellows), generously supported by the Alfred P. Sloan Foundation, aims to improve collaboration and community building in science. It provides a year-long professional development opportunity to individuals who cultivate member engagement and collaborative relationships within scientific associations, research collaborations and other communities of scientists. This book is a collection of blog posts that describe the experiences of many professional community managers. Their stories provide a wealth of knowlege that aspiring and practicing community managers can use. 

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Who / what is a Community Manager? {#who}


## Rational for community managers


## Quick start


You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# What makes a community?

## Diversity of communities

## Community theory

## Tools and technologies

## Putting theory into practice

## Communities in action

<!--chapter:end:02-literature.Rmd-->

# Programming and planning

## creating and planning events

## events how-tos


<!--chapter:end:03-method.Rmd-->

# Building Culture: Inclusive By Default

## CMs as leaders

##  Diversity, Equity, and Inclusion


<!--chapter:end:04-application.Rmd-->

# Conclusion

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

